Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2016-12-01 cbm-rbd-paper.tex
final stuff for submission

We consider the well-known Weibull model for component lifetimes,
which is used in a wide variety of reliability studies \textbf{***more motivation Weibull***}. 
To keep things simple, we assume that the shape parameter of the Weibull distribution is known,
and that only the scale parameter needs to be estimated.
The model could be extended to learn also the shape parameter in a later step,
using, e.g., the discretized approach by \cite{1969:soland}.

@@

Now we can derive the adaptive and dynamic maintenance policy
that resembles a CBM policy.
Consider a set of evaluation time points $\tnow$.
Instead of determining a threshold for a degradation signal like in usual CBM approaches,
we determine, for each present time $\tnow$,
the adaptive and dynamic time span $\tausnow$ which gives the time from $\tnow$ until the optimal moment of maintenance.
Close to system startup, $\tausnow$ will be large;
but as components in the system age and some indeed fail over time,
$\tausnow$ will typically decrease.
%Let $\tprep$ be the time span needed to prepare maintenance work.
%Let $\tthresh$ be a threshold time span chosen for practical reasons.
%used to decide when maintenance is initiated, i.e.,
A preventive maintenance action is initiated
as soon as $\tausnow$ decreases below the time span to the next evaluation time.
%continuing to the the next evaluation point $\tnow$ would carry the risk 
%a time span chosen to reflect operational practicalities.
This dynamic and adaptive maintenance policy is described in more detail in Section~\ref{sec:operationalprocedure};
a graphical overview is given in Figure~\ref{fig:procedure}.

@@

Define a grid of planned evaluation time points as $\{m \delta : m \in \naturals_0\}$,
%where $m = 0, 1, 2, \ldots$,
%and $\delta$ sufficiently small to be negligible on the system lifetime scale.
with $\delta$ a sufficiently small time increment.
During an operational cycle,
$\tausnow$ is recalculated at times $\tnow = m \delta$, $m = 0, 1, 2, \ldots$.
%where the time increment $\delta$ should be small enough to be negligible on the scale of system lifetime.
However, if a component fails before the next $\tnow$ on the grid,
$\tnow$ is set instead to the exact failure time $t_{k,i}$.
Next, we check whether the system has failed due to this component failure.
If the system has failed, a corrective maintenance action is carried out, incurring cost $c_c$.
If the system has not failed, we calculate $\tausnow$ is for the current off-grid time $\tnow = t_{k,i}$,
and move back onto the grid afterwards,
unless there is another component failure before the next planned evaluation time.

>>>>

We consider the well-known Weibull model for component lifetimes,
which is used in a wide variety of reliability studies. 
To keep things simple, we assume that the shape parameter of the Weibull distribution is known,
and that only the scale parameter needs to be estimated.
The model could be extended to learn also the shape parameter in a later step,
using, e.g., the discretized approach by \cite{1969:soland}.

@@

Now we can derive the adaptive and dynamic maintenance policy
that resembles a CBM policy.
Consider a set of evaluation time points $\tnow$.
Instead of determining a threshold for a degradation signal like in usual CBM approaches,
we determine, for each present time $\tnow$,
the adaptive and dynamic time span $\tausnow$ which gives the time from $\tnow$ until the optimal moment of maintenance.
Close to system startup, $\tausnow$ will be large;
but as components in the system age and some indeed fail over time,
$\tausnow$ will typically decrease.
%Let $\tprep$ be the time span needed to prepare maintenance work.
%Let $\tthresh$ be a threshold time span chosen for practical reasons.
%used to decide when maintenance is initiated, i.e.,
A preventive maintenance action is initiated
as soon as $\tausnow$ decreases below the time span to the next evaluation time.
%continuing to the the next evaluation point $\tnow$ would carry the risk 
%a time span chosen to reflect operational practicalities.
This dynamic and adaptive maintenance policy is described in more detail in Section~\ref{sec:operationalprocedure};
a flow chart for the policy is given in Figure~\ref{fig:procedure}.

@@

Define a grid of planned evaluation time points as $\{m \delta : m \in \naturals_0\}$,
%where $m = 0, 1, 2, \ldots$,
%and $\delta$ sufficiently small to be negligible on the system lifetime scale.
with $\delta$ a sufficiently small time increment.
During an operational cycle,
$\tausnow$ is usually recalculated at times $\tnow = m \delta$, $m = 0, 1, 2, \ldots$.
%where the time increment $\delta$ should be small enough to be negligible on the scale of system lifetime.
However, if a component fails before the next $\tnow$ on the grid,
$\tnow$ is set instead to the exact failure time $t_{k,i}$.
Next, we check whether the system has failed due to this component failure.
If the system has failed, a corrective maintenance action is carried out, incurring cost $c_c$.
If the system has not failed, we calculate $\tausnow$ is for the current off-grid time $\tnow = t_{k,i}$,
and move back onto the grid afterwards,
unless there is another component failure before the next planned evaluation time.
